Сравнение областей истинности запросов к реляционной базе данных

### 2015-09-26 SUSU/paper_main.tex
Fixed references numbering.

	\bibitem{afrati}
	\selectlanguageifdefined{english}
	\BibEmph{Afrati,~Foto~N.} Rewriting queries using views in the presence of
	arithmetic comparisons. [Text]~/ Foto~N.~Afrati, Chen~Li, Prasenjit~Mitra~//
	\BibEmph{Theor. Comput. Sci.} ---
	\newblock 2006. ---
	\newblock Vol. 368, no. 1-2. ---
	\newblock P.~88--123.

	\bibitem{baralis}
	\selectlanguageifdefined{english}
	\BibEmph{Baralis,~Elena}. Materialized Views Selection in a Multidimensional
	Database [Text]~/ Elena~Baralis, Stefano~Paraboschi, Ernest~Teniente~//
	Proceedings of the 23rd International Conference on Very Large Data Bases.
	---
	\newblock VLDB '97. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1997. ---
	\newblock P.~156--165. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645923.671019}.

	\bibitem{church}
	\selectlanguageifdefined{english}
	\BibEmph{Church,~Alonzo}. Introduction to Mathematical Logic [Text]~/
	Alonzo~Church. ---
	\newblock [S.\ l.]~: Princeton University Press, 1996. ---
	\newblock 378~p.

	\bibitem{date}
	\selectlanguageifdefined{english}
	\BibEmph{Date,~Christopher~J.} SQL and Relational Theory [Text]~/
	Christopher~J.~Date. ---
	\newblock [S.\ l.]~: O'Reilly, 2009. ---
	\newblock 448~p.

	\bibitem{denny}
	\selectlanguageifdefined{english}
	\BibEmph{Denny,~Matthew}.
	\href{http://dx.doi.org/10.1145/1066157.1066231}{Predicate Result Range
		Caching for Continuous Queries} [Text]~/ Matthew~Denny,
	Michael~J.~Franklin~// Proceedings of the 2005 ACM SIGMOD International
	Conference on Management of Data. ---
	\newblock SIGMOD '05. ---
	\newblock New York, NY, USA~: ACM, 2005. ---
	\newblock P.~646--657. ---
	\newblock URL: \BibUrl{http://doi.acm.org/10.1145/1066157.1066231}.

	\bibitem{gupta97}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~Himanshu}. Selection of Views to Materialize in a Data
	Warehouse [Text]~/ Himanshu~Gupta~// Proceedings of the 6th International
	Conference on Database Theory. ---
	\newblock ICDT '97. ---
	\newblock London, UK, UK~: Springer-Verlag, 1997. ---
	\newblock P.~98--112. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645502.656089}.

	\bibitem{gupta99}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~Himanshu}. Selection of Views to Materialize Under a
	Maintenance Cost Constraint [Text]~/ Himanshu~Gupta, Inderpal~Singh~Mumick~//
	Proceedings of the 7th International Conference on Database Theory. ---
	\newblock ICDT '99. ---
	\newblock London, UK, UK~: Springer-Verlag, 1999. ---
	\newblock P.~453--470. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645503.656261}.

	\bibitem{hilbert}
	\selectlanguageifdefined{english}
	\BibEmph{Hilbert,~David}. Principles of Mathematical Logic [Text]~/
	David~Hilbert, Wilhelm~Ackermann. ---
	\newblock [S.\ l.]~: AMS Chelsea Publishing, 1950. ---
	\newblock 172~p.

	\bibitem{kalnis}
	\selectlanguageifdefined{english}
	\BibEmph{Kalnis,~Panos}. Proxy-Server Architectures for OLAP. [Text]~/
	Panos~Kalnis, Dimitris~Papadias~// SIGMOD Conference~/ Ed.\ by\
	Sharad~Mehrotra, Timos~K.~Sellis. ---
	\newblock [S.\ l.]~: ACM, 2001. ---
	\newblock P.~367--378.

	\bibitem{keller}
	\selectlanguageifdefined{english}
	\BibEmph{Keller,~Arthur~M.} A Predicate-based Caching Scheme for Client-Server
	Database Architectures [Text]~/ Arthur~M.~Keller, Julie~Basu~// \BibEmph{VLDB
		J.} ---
	\newblock 1996. ---
	\newblock Vol.~5, no.~1. ---
	\newblock P.~35--47.

	\bibitem{mendelson}
	\selectlanguageifdefined{english}
	\BibEmph{Mendelson,~Elliott}. Introduction to Mathematical Logic [Text]~/
	Elliott~Mendelson. ---
	\newblock 5 edition. ---
	\newblock [S.\ l.]~: CRC Press, 2009. ---
	\newblock 469~p.

	\bibitem{mosin_zykin}
	\selectlanguageifdefined{english}
	\BibEmph{Mosin,~Sergey}. Truth space method for caching database queries
	[Text]~/ Sergey~Mosin, Sergey~Zykin~// \BibEmph{Modeling and Analysis of
		Information Systems}. ---
	\newblock 2015. ---
	\newblock Vol.~22, no.~2. ---
	\newblock P.~248--258.

	\bibitem{olston}
	\selectlanguageifdefined{english}
	\BibEmph{Olston,~Chris}.
	\href{http://dx.doi.org/10.1145/872757.872825}{Adaptive Filters for
		Continuous Queries over Distributed Data Streams} [Text]~/ Chris~Olston,
	Jing~Jiang, Jennifer~Widom~// Proceedings of the 2003 ACM SIGMOD
	International Conference on Management of Data. ---
	\newblock SIGMOD '03. ---
	\newblock New York, NY, USA~: ACM, 2003. ---
	\newblock P.~563--574. ---
	\newblock URL: \BibUrl{http://doi.acm.org/10.1145/872757.872825}.

	\bibitem{chang}
	\selectlanguageifdefined{english}
	\BibEmph{Park,~Chang-Sup}. Usability-based caching of query results in OLAP
	systems. [Text]~/ Chang-Sup~Park, Myoung-Ho~Kim, Yoon-Joon~Lee~//
	\BibEmph{Journal of Systems and Software}. ---
	\newblock 2003. ---
	\newblock Vol.~68, no.~2. ---
	\newblock P.~103--119.

	\bibitem{scheuermann}
	\selectlanguageifdefined{english}
	\BibEmph{Scheuermann,~Peter}. WATCHMAN: A Data Warehouse Intelligent Cache
	Manager [Text]~/ Peter~Scheuermann, Junho~Shim, Radek~Vingralek~//
	Proceedings of the 22th International Conference on Very Large Data Bases.
	---
	\newblock VLDB '96. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1996. ---
	\newblock P.~51--62. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645922.758367}.

	\bibitem{shim}
	\selectlanguageifdefined{english}
	\BibEmph{Shim,~Junho}. Dynamic Caching of Query Results for Decision Support
	Systems. [Text]~/ Junho~Shim, Peter~Scheuermann, Radek~Vingralek~// SSDBM.
	---
	\newblock [S.\ l.~: s.\ n.], 1999. ---
	\newblock P.~254--263.
\end{biblio}

@@

	\bibitem{afrati}
	\selectlanguageifdefined{english}
	\BibEmph{Afrati,~Foto~N.} Rewriting queries using views in the presence of
	arithmetic comparisons. [Text]~/ Foto~N.~Afrati, Chen~Li, Prasenjit~Mitra~//
	\BibEmph{Theor. Comput. Sci.} ---
	\newblock 2006. ---
	\newblock Vol. 368, no. 1-2. ---
	\newblock P.~88--123.

	\bibitem{baralis}
	\selectlanguageifdefined{english}
	\BibEmph{Baralis,~Elena}. Materialized Views Selection in a Multidimensional
	Database [Text]~/ Elena~Baralis, Stefano~Paraboschi, Ernest~Teniente~//
	Proceedings of the 23rd International Conference on Very Large Data Bases.
	---
	\newblock VLDB '97. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1997. ---
	\newblock P.~156--165. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645923.671019}.

	\bibitem{church}
	\selectlanguageifdefined{english}
	\BibEmph{Church,~Alonzo}. Introduction to Mathematical Logic [Text]~/
	Alonzo~Church. ---
	\newblock [S.\ l.]~: Princeton University Press, 1996. ---
	\newblock 378~p.

	\bibitem{date}
	\selectlanguageifdefined{english}
	\BibEmph{Date,~Christopher~J.} SQL and Relational Theory [Text]~/
	Christopher~J.~Date. ---
	\newblock [S.\ l.]~: O'Reilly, 2009. ---
	\newblock 448~p.

	\bibitem{denny}
	\selectlanguageifdefined{english}
	\BibEmph{Denny,~Matthew}.
	\href{http://dx.doi.org/10.1145/1066157.1066231}{Predicate Result Range
		Caching for Continuous Queries} [Text]~/ Matthew~Denny,
	Michael~J.~Franklin~// Proceedings of the 2005 ACM SIGMOD International
	Conference on Management of Data. ---
	\newblock SIGMOD '05. ---
	\newblock New York, NY, USA~: ACM, 2005. ---
	\newblock P.~646--657. ---
	\newblock URL: \BibUrl{http://doi.acm.org/10.1145/1066157.1066231}.

	\bibitem{gupta97}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~Himanshu}. Selection of Views to Materialize in a Data
	Warehouse [Text]~/ Himanshu~Gupta~// Proceedings of the 6th International
	Conference on Database Theory. ---
	\newblock ICDT '97. ---
	\newblock London, UK, UK~: Springer-Verlag, 1997. ---
	\newblock P.~98--112. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645502.656089}.

	\bibitem{gupta99}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~Himanshu}. Selection of Views to Materialize Under a
	Maintenance Cost Constraint [Text]~/ Himanshu~Gupta, Inderpal~Singh~Mumick~//
	Proceedings of the 7th International Conference on Database Theory. ---
	\newblock ICDT '99. ---
	\newblock London, UK, UK~: Springer-Verlag, 1999. ---
	\newblock P.~453--470. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645503.656261}.

	\bibitem{hilbert}
	\selectlanguageifdefined{english}
	\BibEmph{Hilbert,~David}. Principles of Mathematical Logic [Text]~/
	David~Hilbert, Wilhelm~Ackermann. ---
	\newblock [S.\ l.]~: AMS Chelsea Publishing, 1950. ---
	\newblock 172~p.

	\bibitem{kalnis}
	\selectlanguageifdefined{english}
	\BibEmph{Kalnis,~Panos}. Proxy-Server Architectures for OLAP. [Text]~/
	Panos~Kalnis, Dimitris~Papadias~// SIGMOD Conference~/ Ed.\ by\
	Sharad~Mehrotra, Timos~K.~Sellis. ---
	\newblock [S.\ l.]~: ACM, 2001. ---
	\newblock P.~367--378.

	\bibitem{keller}
	\selectlanguageifdefined{english}
	\BibEmph{Keller,~Arthur~M.} A Predicate-based Caching Scheme for Client-Server
	Database Architectures [Text]~/ Arthur~M.~Keller, Julie~Basu~// \BibEmph{VLDB
		J.} ---
	\newblock 1996. ---
	\newblock Vol.~5, no.~1. ---
	\newblock P.~35--47.

	\bibitem{mendelson}
	\selectlanguageifdefined{english}
	\BibEmph{Mendelson,~Elliott}. Introduction to Mathematical Logic [Text]~/
	Elliott~Mendelson. ---
	\newblock 5 edition. ---
	\newblock [S.\ l.]~: CRC Press, 2009. ---
	\newblock 469~p.

	\bibitem{mosin_zykin}
	\selectlanguageifdefined{english}
	\BibEmph{Mosin,~Sergey}. Truth space method for caching database queries
	[Text]~/ Sergey~Mosin, Sergey~Zykin~// \BibEmph{Modeling and Analysis of
		Information Systems}. ---
	\newblock 2015. ---
	\newblock Vol.~22, no.~2. ---
	\newblock P.~248--258.

	\bibitem{olston}
	\selectlanguageifdefined{english}
	\BibEmph{Olston,~Chris}.
	\href{http://dx.doi.org/10.1145/872757.872825}{Adaptive Filters for
		Continuous Queries over Distributed Data Streams} [Text]~/ Chris~Olston,
	Jing~Jiang, Jennifer~Widom~// Proceedings of the 2003 ACM SIGMOD
	International Conference on Management of Data. ---
	\newblock SIGMOD '03. ---
	\newblock New York, NY, USA~: ACM, 2003. ---
	\newblock P.~563--574. ---
	\newblock URL: \BibUrl{http://doi.acm.org/10.1145/872757.872825}.

	\bibitem{chang}
	\selectlanguageifdefined{english}
	\BibEmph{Park,~Chang-Sup}. Usability-based caching of query results in OLAP
	systems. [Text]~/ Chang-Sup~Park, Myoung-Ho~Kim, Yoon-Joon~Lee~//
	\BibEmph{Journal of Systems and Software}. ---
	\newblock 2003. ---
	\newblock Vol.~68, no.~2. ---
	\newblock P.~103--119.

	\bibitem{scheuermann}
	\selectlanguageifdefined{english}
	\BibEmph{Scheuermann,~Peter}. WATCHMAN: A Data Warehouse Intelligent Cache
	Manager [Text]~/ Peter~Scheuermann, Junho~Shim, Radek~Vingralek~//
	Proceedings of the 22th International Conference on Very Large Data Bases.
	---
	\newblock VLDB '96. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1996. ---
	\newblock P.~51--62. ---
	\newblock URL: \BibUrl{http://dl.acm.org/citation.cfm?id=645922.758367}.

	\bibitem{shim}
	\selectlanguageifdefined{english}
	\BibEmph{Shim,~Junho}. Dynamic Caching of Query Results for Decision Support
	Systems. [Text]~/ Junho~Shim, Peter~Scheuermann, Radek~Vingralek~// SSDBM.
	---
	\newblock [S.\ l.~: s.\ n.], 1999. ---
	\newblock P.~254--263.
\end{biblio_lat}

>>>>

	\bibitem{afrati}
	\selectlanguageifdefined{english}
	\BibEmph{Afrati,~F.~N.} Rewriting queries using views in the presence of
	arithmetic comparisons. ~/ F.~N.~Afrati, C.~Li, P.~Mitra~//
	\BibEmph{Theor. Comput. Sci.} ---
	\newblock 2006. ---
	\newblock Vol. 368, No. 1-2. ---
	\newblock P.~88--123.

	\bibitem{baralis}
	\selectlanguageifdefined{english}
	\BibEmph{Baralis,~E.} Materialized Views Selection in a Multidimensional
	Database ~/ E.~Baralis, S.~Paraboschi, E.~Teniente~//
	Proceedings of the 23rd International Conference on Very Large Data Bases.
	---
	\newblock VLDB '97. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1997. ---
	\newblock P.~156--165.

	\bibitem{church}
	\selectlanguageifdefined{english}
	\BibEmph{Church,~A.} Introduction to Mathematical Logic ~/
	A.~Church. ---
	\newblock [S.\ l.]~: Princeton University Press, 1996. ---
	\newblock 378~p.

	\bibitem{date}
	\selectlanguageifdefined{english}
	\BibEmph{Date,~C.~J.} SQL and Relational Theory ~/
	C.~J.~Date. ---
	\newblock [S.\ l.]~: O'Reilly, 2009. ---
	\newblock 448~p.

	\bibitem{denny}
	\selectlanguageifdefined{english}
	\BibEmph{Denny,~M.}
	\href{http://dx.doi.org/10.1145/1066157.1066231}{Predicate Result Range
		Caching for Continuous Queries} ~/ M.~Denny,
	M.~J.~Franklin~// Proceedings of the 2005 ACM SIGMOD International
	Conference on Management of Data. ---
	\newblock SIGMOD '05. ---
	\newblock New York, NY, USA~: ACM, 2005. ---
	\newblock P.~646--657.

	\bibitem{gupta97}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~H.} Selection of Views to Materialize in a Data
	Warehouse ~/ H.~Gupta~// Proceedings of the 6th International
	Conference on Database Theory. ---
	\newblock ICDT '97. ---
	\newblock London, UK, UK~: Springer-Verlag, 1997. ---
	\newblock P.~98--112.

	\bibitem{gupta99}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~H} Selection of Views to Materialize Under a
	Maintenance Cost Constraint ~/ H.~Gupta, Inderpal~Singh~Mumick~//
	Proceedings of the 7th International Conference on Database Theory. ---
	\newblock ICDT '99. ---
	\newblock London, UK, UK~: Springer-Verlag, 1999. ---
	\newblock P.~453--470.

	\bibitem{hilbert}
	\selectlanguageifdefined{english}
	\BibEmph{Hilbert,~D.} Principles of Mathematical Logic ~/
	D.~Hilbert, Wilhelm~Ackermann. ---
	\newblock [S.\ l.]~: AMS Chelsea Publishing, 1950. ---
	\newblock 172~p.

	\bibitem{kalnis}
	\selectlanguageifdefined{english}
	\BibEmph{Kalnis,~P.} Proxy-Server Architectures for OLAP. ~/
	P.~Kalnis, D.~Papadias~// SIGMOD Conference~/ Ed.\ by\
	Sharad~Mehrotra, Timos~K.~Sellis. ---
	\newblock [S.\ l.]~: ACM, 2001. ---
	\newblock P.~367--378.

	\bibitem{keller}
	\selectlanguageifdefined{english}
	\BibEmph{Keller,~A.~M.} A Predicate-based Caching Scheme for Client-Server
	Database Architectures ~/ A.~M.~Keller, J.~Basu~// \BibEmph{VLDB
		J.} ---
	\newblock 1996. ---
	\newblock Vol.~5, No.~1. ---
	\newblock P.~35--47.

	\bibitem{mendelson}
	\selectlanguageifdefined{english}
	\BibEmph{Mendelson,~E.} Introduction to Mathematical Logic ~/
	E.~Mendelson. ---
	\newblock 5 edition. ---
	\newblock [S.\ l.]~: CRC Press, 2009. ---
	\newblock 469~p.

	\bibitem{mosin_zykin}
	\selectlanguageifdefined{english}
	\BibEmph{Mosin,~S.} Truth space method for caching database queries
	~/ S.~Mosin, S.~Zykin~// \BibEmph{Modeling and Analysis of
		Information Systems}. ---
	\newblock 2015. ---
	\newblock Vol.~22, No.~2. ---
	\newblock P.~248--258.

	\bibitem{olston}
	\selectlanguageifdefined{english}
	\BibEmph{Olston,~C.}
	\href{http://dx.doi.org/10.1145/872757.872825}{Adaptive Filters for
		Continuous Queries over Distributed Data Streams} ~/ C.~Olston,
	J.~Jiang, J.~Widom~// Proceedings of the 2003 ACM SIGMOD
	International Conference on Management of Data. ---
	\newblock SIGMOD '03. ---
	\newblock New York, NY, USA~: ACM, 2003. ---
	\newblock P.~563--574.

	\bibitem{chang}
	\selectlanguageifdefined{english}
	\BibEmph{Park,~C.} Usability-based caching of query results in OLAP
	systems. ~/ C.~Park, M.~Kim, Y.~Lee~//
	\BibEmph{Journal of Systems and Software}. ---
	\newblock 2003. ---
	\newblock Vol.~68, No.~2. ---
	\newblock P.~103--119.

	\bibitem{scheuermann}
	\selectlanguageifdefined{english}
	\BibEmph{Scheuermann,~P.} WATCHMAN: A Data Warehouse Intelligent Cache
	Manager ~/ P.~Scheuermann, J.~Shim, R.~Vingralek~//
	Proceedings of the 22th International Conference on Very Large Data Bases.
	---
	\newblock VLDB '96. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1996. ---
	\newblock P.~51--62.

	\bibitem{shim}
	\selectlanguageifdefined{english}
	\BibEmph{Shim,~J.} Dynamic Caching of Query Results for Decision Support
	Systems. ~/ J.~Shim, P.~Scheuermann, R.~Vingralek~// SSDBM.
	---
	\newblock [S.\ l.~: s.\ n.], 1999. ---
	\newblock P.~254--263.
\end{biblio}

@@

	\bibitem{afrati}
	\selectlanguageifdefined{english}
	\BibEmph{Afrati,~F.~N.} Rewriting queries using views in the presence of
	arithmetic comparisons. ~/ F.~N.~Afrati, C.~Li, P.~Mitra~//
	\BibEmph{Theor. Comput. Sci.} ---
	\newblock 2006. ---
	\newblock Vol. 368, No. 1-2. ---
	\newblock P.~88--123.

	\bibitem{baralis}
	\selectlanguageifdefined{english}
	\BibEmph{Baralis,~E.} Materialized Views Selection in a Multidimensional
	Database ~/ E.~Baralis, S.~Paraboschi, E.~Teniente~//
	Proceedings of the 23rd International Conference on Very Large Data Bases.
	---
	\newblock VLDB '97. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1997. ---
	\newblock P.~156--165.

	\bibitem{church}
	\selectlanguageifdefined{english}
	\BibEmph{Church,~A.} Introduction to Mathematical Logic ~/
	A.~Church. ---
	\newblock [S.\ l.]~: Princeton University Press, 1996. ---
	\newblock 378~p.

	\bibitem{date}
	\selectlanguageifdefined{english}
	\BibEmph{Date,~C.~J.} SQL and Relational Theory ~/
	C.~J.~Date. ---
	\newblock [S.\ l.]~: O'Reilly, 2009. ---
	\newblock 448~p.

	\bibitem{denny}
	\selectlanguageifdefined{english}
	\BibEmph{Denny,~M.}
	\href{http://dx.doi.org/10.1145/1066157.1066231}{Predicate Result Range
		Caching for Continuous Queries} ~/ M.~Denny,
	M.~J.~Franklin~// Proceedings of the 2005 ACM SIGMOD International
	Conference on Management of Data. ---
	\newblock SIGMOD '05. ---
	\newblock New York, NY, USA~: ACM, 2005. ---
	\newblock P.~646--657.

	\bibitem{gupta97}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~H.} Selection of Views to Materialize in a Data
	Warehouse ~/ H.~Gupta~// Proceedings of the 6th International
	Conference on Database Theory. ---
	\newblock ICDT '97. ---
	\newblock London, UK, UK~: Springer-Verlag, 1997. ---
	\newblock P.~98--112.

	\bibitem{gupta99}
	\selectlanguageifdefined{english}
	\BibEmph{Gupta,~H} Selection of Views to Materialize Under a
	Maintenance Cost Constraint ~/ H.~Gupta, Inderpal~Singh~Mumick~//
	Proceedings of the 7th International Conference on Database Theory. ---
	\newblock ICDT '99. ---
	\newblock London, UK, UK~: Springer-Verlag, 1999. ---
	\newblock P.~453--470.

	\bibitem{hilbert}
	\selectlanguageifdefined{english}
	\BibEmph{Hilbert,~D.} Principles of Mathematical Logic ~/
	D.~Hilbert, Wilhelm~Ackermann. ---
	\newblock [S.\ l.]~: AMS Chelsea Publishing, 1950. ---
	\newblock 172~p.

	\bibitem{kalnis}
	\selectlanguageifdefined{english}
	\BibEmph{Kalnis,~P.} Proxy-Server Architectures for OLAP. ~/
	P.~Kalnis, D.~Papadias~// SIGMOD Conference~/ Ed.\ by\
	Sharad~Mehrotra, Timos~K.~Sellis. ---
	\newblock [S.\ l.]~: ACM, 2001. ---
	\newblock P.~367--378.

	\bibitem{keller}
	\selectlanguageifdefined{english}
	\BibEmph{Keller,~A.~M.} A Predicate-based Caching Scheme for Client-Server
	Database Architectures ~/ A.~M.~Keller, J.~Basu~// \BibEmph{VLDB
		J.} ---
	\newblock 1996. ---
	\newblock Vol.~5, No.~1. ---
	\newblock P.~35--47.

	\bibitem{mendelson}
	\selectlanguageifdefined{english}
	\BibEmph{Mendelson,~E.} Introduction to Mathematical Logic ~/
	E.~Mendelson. ---
	\newblock 5 edition. ---
	\newblock [S.\ l.]~: CRC Press, 2009. ---
	\newblock 469~p.

	\bibitem{mosin_zykin}
	\selectlanguageifdefined{english}
	\BibEmph{Mosin,~S.} Truth space method for caching database queries
	~/ S.~Mosin, S.~Zykin~// \BibEmph{Modeling and Analysis of
		Information Systems}. ---
	\newblock 2015. ---
	\newblock Vol.~22, No.~2. ---
	\newblock P.~248--258.

	\bibitem{olston}
	\selectlanguageifdefined{english}
	\BibEmph{Olston,~C.}
	\href{http://dx.doi.org/10.1145/872757.872825}{Adaptive Filters for
		Continuous Queries over Distributed Data Streams} ~/ C.~Olston,
	J.~Jiang, J.~Widom~// Proceedings of the 2003 ACM SIGMOD
	International Conference on Management of Data. ---
	\newblock SIGMOD '03. ---
	\newblock New York, NY, USA~: ACM, 2003. ---
	\newblock P.~563--574.

	\bibitem{chang}
	\selectlanguageifdefined{english}
	\BibEmph{Park,~C.} Usability-based caching of query results in OLAP
	systems. ~/ C.~Park, M.~Kim, Y.~Lee~//
	\BibEmph{Journal of Systems and Software}. ---
	\newblock 2003. ---
	\newblock Vol.~68, No.~2. ---
	\newblock P.~103--119.

	\bibitem{scheuermann}
	\selectlanguageifdefined{english}
	\BibEmph{Scheuermann,~P.} WATCHMAN: A Data Warehouse Intelligent Cache
	Manager ~/ P.~Scheuermann, J.~Shim, R.~Vingralek~//
	Proceedings of the 22th International Conference on Very Large Data Bases.
	---
	\newblock VLDB '96. ---
	\newblock San Francisco, CA, USA~: Morgan Kaufmann Publishers Inc., 1996. ---
	\newblock P.~51--62.

	\bibitem{shim}
	\selectlanguageifdefined{english}
	\BibEmph{Shim,~J.} Dynamic Caching of Query Results for Decision Support
	Systems. ~/ J.~Shim, P.~Scheuermann, R.~Vingralek~// SSDBM.
	---
	\newblock [S.\ l.~: s.\ n.], 1999. ---
	\newblock P.~254--263.
\end{biblio_lat}
